\subsection{SIRAH Simulations}

All atomistic structures of peptides were generated using an in-house VMD script\cite{VMD} and minimized in CHARMM36m force field\cite{CHARMM36m}. Cysteine residues involved in disulfide bonds were converted to CYX type prior to CG mapping.
Topologies and coordinate files were generated using the SIRAH tools\cite{SIRAH2.0}, and backbone restraints were included during equilibration via custom itp files generated using GROMACS software package (versions 2020.4 and 2022.1)\cite{GROMACS,GROMACS2}.

Coarse-grained (CG) molecular dynamics simulations were performed using the SIRAH 2.0 force field for proteins\cite{SIRAH2.0} and the WT4 model for water, with corresponding SIRAH models for ions\cite{SIRAHWT}.
All simulations were carried out with the GROMACS software package (versions 2020.4 and 2022.1)\cite{GROMACS,GROMACS2}.

For disulfide-linked peptides, a total of 150 CG peptide molecules were inserted into a cubic simulation box of 13 nm per side, ensuring a minimum distance of 0.5 nm between molecules.
For monomeric peptides, 300 copies were used.
The system was solvated with WT4 water beads, and neutralized with NaW and ClW ions as needed.
The initial configuration was subjected to a two-step energy minimization (15,000 steps each, steepest descent algorithm, emtol 1.0 kJ$\cdot$mol$^{-1}\cdot$nm$^{-1}$, emstep 0.05 nm).

Following minimization, the system underwent a 2 ns NPT equilibration to condense the solvent (dt = 2 fs, 200,000 steps, V-rescale thermostat, $\tau_t$ = 2 ps, Parrinello-Rahman barostat, $\tau_p$ = 8 ps, compressibility = $4.5 \times 10^{-5}$ bar$^{-1}$, reference pressure 1 bar).
This was followed by two NVT equilibration steps: 5 ns (dt = 20 fs, 100,000 steps, $\tau_t$ = 1 ps) and 25 ns (dt = 20 fs, 1,250,000 steps, $\tau_t$ = 1 ps), both at 300 K.
During equilibration, backbone positional restraints (1000 kJ$\cdot$mol$^{-1}\cdot$nm$^{-2}$) were applied to all protein beads.

Production simulations were performed in the NPT ensemble for 0.5 $\mu$s (dt = 20 fs, 25,000,000 steps) at 300 K and 1 bar, using the V-rescale thermostat ($\tau_t$ = 2 ps) and Parrinello-Rahman barostat ($\tau_p$ = 8 ps).
Electrostatic interactions were treated with the smooth particle-mesh Ewald (PME) method\cite{PME,PMEEssmann}, with a real-space cutoff of 1.2 nm.
Lennard-Jones interactions were cut off at 1.2 nm.
Neighbor searching was performed using a grid algorithm with a cutoff of 1.2 nm and an update frequency of 10 steps (100 steps for production).
The leap-frog integrator was used throughout\cite{Leap-frog}.








